Enhancement of SDR in Thessaloniki

### 2024-03-08 GHI_enh_04_investigate.tex
Commit 2024-03-07 13:13
Commit 2024-03-08 12:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-07}

@@

lmD: 1467.857 +/- 152.6559

lmY: 1467.88 +/- 152.6586

Arima: 1467.8769 184.2435 7.967 0

@@

@@

\begin{verbatim}
2024-03-07 09:37:46.8 athan@tyler GHI_enh_04_investigate.R 1.373684 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-08}

@@

lmD: 1.467857 +/- 0.1526559

lmY: 1.46788 +/- 0.1526586

Arima: 1.4679 0.1843 7.9642 0

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-37} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-38} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-39} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza_month-40} \end{center}

@@

\begin{verbatim}
2024-03-08 08:30:44.9 athan@tyler GHI_enh_04_investigate.R 1.934441 mins
\end{verbatim}
